---
title: "Assignment_5"
author: "Joyce Aldrich"
date: "2022-10-15"
output:
  html_document: default
---
# Assignment
# Pick three of your favorite books on one of your favorite subjects. At least one of the books should have more
# than one author. For each book, include the title, authors, and two or three other attributes that you find
# interesting.
# Take the information that you’ve selected about these three books, and separately create three files which
# store the book’s information in HTML (using an html table), XML, and JSON formats (e.g. “books.html”,
# “books.xml”, and “books.json”). To help you better understand the different file structures, I’d prefer that you
# create each of these files “by hand” unless you’re already very comfortable with the file formats.

#install packages into R
# XML / RJSON

#1
# HTML file 
# Loading html file into R
```{r}
library(XML)
books_html_table <- readHTMLTable("/Users/joycealdrich/Documents/SPS Data Science/Data 607/Assignment_5/Books.html", which = 1)
head(books_html_table)
```
#2 
#XML file
#loadin XML file into R and turn into df

```{r}
library(XML)
xml_parsed<-xmlParse(file = "/Users/joycealdrich/Documents/SPS Data Science/Data 607/Assignment_5/Books.xml")
books_xml_table<-xmlToDataFrame(xml_parsed, stringsAsFactors = FALSE)                       
head(books_xml_table)
```
#3
#json
#loading json file into R
```{r}
library(rjson)
json_parsed <-fromJSON(file = "/Users/joycealdrich/Documents/SPS Data Science/Data 607/Assignment_5/Books.json")
print(json_parsed)
books_json_table<- as.data.frame(json_parsed)
head(books_json_table)

```


